# Data

We will use the same dataset: [`movies_merged`](https://s3.amazonaws.com/content.udacity-data.com/courses/gt-cs6242/project/movies_merged).

# Objective

The goal is to build a linear regression model that can predict the `Gross` revenue earned by a movie based on other variables. 

# Setup

Load the dataset into memory:

```{r}
load('movies_merged')
```

This creates an object of the same name (`movies_merged`). For convenience, you can copy it to `df` and start using it:

```{r}
df = movies_merged
cat("Dataset has", dim(df)[1], "rows and", dim(df)[2], "columns", end="\n", file="")
colnames(df)
```

## Load R packages

Load any R packages that you will need to use. 

```{r}
library(ggplot2)
library(GGally)
library(NLP)
library(tm)
library(stringr)
library(tidyr)
library(xlsx)
library(MASS)
```

# Data Preprocessing

Before we start building models, we should clean up the dataset and perform any preprocessing steps that may be necessary. 

## 1. Remove non-movie rows

```{r}
# Remove all rows from df that do not correspond to movies
df=df[df$Type=="movie", ]#40000rows remained
```

## 2. Drop rows with missing `Gross` value

Since our goal is to model `Gross` revenue against other variables, rows that have missing `Gross` values are not useful to us.

```{r}
# Remove rows with missing Gross value
df=df[!is.na(df$Gross),]
```

## 3. Exclude movies released prior to 2000

Inflation and other global financial factors may affect the revenue earned by movies during certain periods of time. Taking that into account is out of scope for this project, so let's exclude all movies that were released prior to the year 2000 (you may use `Released`, `Date` or `Year` for this purpose).

```{r}
# Exclude movies released prior to 2000
df<-df[!(df$Year<=2000),] #I used 'Year'
```

## 4. Eliminate mismatched rows

_Note: You may compare the `Released` column (string representation of release date) with either `Year` or `Date` (numeric representation of the year) to find mismatches. The goal is to avoid removing more than 10% of the rows._

```{r}
# Remove mismatched rows
#avoid removing more than 3163*0.1 rows
subsetmatch <- subset(df, as.numeric(substr(df$Released,1,4))-as.numeric(df$Year)<=1) # remaining 3050 rows
#3163-3050=113 rows were deleted
```

## 5. Drop `Domestic_Gross` column

`Domestic_Gross` is basically the amount of revenue a movie earned within the US. Understandably, it is very highly correlated with `Gross` and is in fact equal to it for movies that were not released globally. Hence, it should be removed for modeling purposes.

```{r}
# Exclude the `Domestic_Gross` column
subsetmatch <- subset(subsetmatch, select = -Domestic_Gross)
```

## 6. Process `Runtime` column

```{r}
# Replace df$Runtime with a numeric column containing the runtime in minutes
df <- subsetmatch
df$Runtime[df$Runtime=="1 h"] <- "60 min"#change runtime 1 h to be 60 min
df=df[df$Runtime!="N/A",]#remove columns without runtime, 3050-3026=24 rows removed
df$newtime <- str_extract_all(df$Runtime,"\\(?[0-9,.]+\\)?",simplify = TRUE)#extract runtime as seperate numbers, and there is only mins in the column
df$Runtime <- df$newtime#replace runtime with newtime
df <- subset(df, select = -newtime) #delete column newtime 
```

Perform any additional preprocessing steps that you find necessary, such as dealing with missing values or highly correlated columns (feel free to add more code chunks, markdown blocks and plots here as necessary).

```{r}
# Additional preprocessing
#since tomatoreviews=tomatofresh+tomatorotten, I will delete the tomatoRotten column
df <- subset(df, select = -tomatoRotten)
#since year and date have the same data, I will delete the Date column
df <- subset(df, select = -Date)

```

## Final preprocessed dataset

Report the dimensions of the preprocessed dataset you will be using for modeling and evaluation, and print all the final column names. (Again, `Domestic_Gross` should not be in this list!)

```{r}
# Print the dimensions of the final preprocessed dataset and column names
cat("Dataset has", dim(df)[1], "rows and", dim(df)[2], "columns", end="\n", file="")
colnames(df)
```

# Evaluation Strategy

In each of the tasks described in the next section, you will build a regression model. In order to compare their performance, use the following evaluation procedure every time:

1. Randomly divide the rows into two sets of sizes 5% and 95%.
2. Use the first set for training and the second for testing.
3. Compute the Root Mean Squared Error (RMSE) on the train and test sets.
4. Repeat the above data partition and model training and evaluation 10 times and average the RMSE results so the results stabilize.
5. Repeat the above steps for different proportions of train and test sizes: 10%-90%, 15%-85%, ..., 95%-5% (total 19 splits including the initial 5%-95%).
6. Generate a graph of the averaged train and test RMSE as a function of the train set size (%).

You can define a helper function that applies this procedure to a given model and reuse it.

# Tasks

Each of the following tasks is worth 20 points. Remember to build each model as specified, evaluate it using the strategy outlined above, and plot the training and test errors by training set size (%).

## 1. Numeric variables

Use linear regression to predict `Gross` based on all available _numeric_ variables.

```{r}
# Build & evaluate model 1 (numeric variables only)
df$Runtime <- as.numeric(df$Runtime)
df$Metascore <- as.numeric(df$Metascore)
df$index<-1:nrow(df)
df$index <- as.numeric(df$index)
nums <- sapply(df, is.numeric)
df_numeric  <- df[ , nums] #df_numeric keep only numeric variables
df_numeric <- na.omit(df_numeric) #deleted rows with NA, remains 2614 rows
df_numeric <- merge(df_numeric, df, by="index")
colnames(df_numeric)[colnames(df_numeric)=="Year.x"] <- "Year"
colnames(df_numeric)[colnames(df_numeric)=="Runtime.x"] <- "Runtime"
colnames(df_numeric)[colnames(df_numeric)=="Metascore.x"] <- "Metascore"
colnames(df_numeric)[colnames(df_numeric)=="imdbRating.x"] <- "imdbRating"
colnames(df_numeric)[colnames(df_numeric)=="imdbVotes.x"] <- "imdbVotes"
colnames(df_numeric)[colnames(df_numeric)=="tomatoMeter.x"] <- "tomatoMeter"
colnames(df_numeric)[colnames(df_numeric)=="tomatoRating.x"] <- "tomatoRating"
colnames(df_numeric)[colnames(df_numeric)=="tomatoReviews.x"] <- "tomatoReviews"
colnames(df_numeric)[colnames(df_numeric)=="tomatoFresh.x"] <- "tomatoFresh"
colnames(df_numeric)[colnames(df_numeric)=="tomatoUserMeter.x"] <- "tomatoUserMeter"
colnames(df_numeric)[colnames(df_numeric)=="tomatoUserRating.x"] <- "tomatoUserRating"
colnames(df_numeric)[colnames(df_numeric)=="tomatoUserReviews.x"] <- "tomatoUserReviews"
colnames(df_numeric)[colnames(df_numeric)=="Budget.x"] <- "Budget"
colnames(df_numeric)[colnames(df_numeric)=="Gross.x"] <- "Gross"
df_numeric <- subset(df_numeric, select = -Year.y)
df_numeric <- subset(df_numeric, select = -Runtime.y)
df_numeric <- subset(df_numeric, select = -Metascore.y)
df_numeric <- subset(df_numeric, select = -imdbRating.y)
df_numeric <- subset(df_numeric, select = -imdbVotes.y)
df_numeric <- subset(df_numeric, select = -tomatoMeter.y)
df_numeric <- subset(df_numeric, select = -tomatoRating.y)
df_numeric <- subset(df_numeric, select = -tomatoReviews.y)
df_numeric <- subset(df_numeric, select = -tomatoFresh.y)
df_numeric <- subset(df_numeric, select = -tomatoUserMeter.y)
df_numeric <- subset(df_numeric, select = -tomatoUserRating.y)
df_numeric <- subset(df_numeric, select = -tomatoUserReviews.y)
df_numeric <- subset(df_numeric, select = -Budget.y)
df_numeric <- subset(df_numeric, select = -Gross.y)
#colnames(df_numeric)
getaverageRMSE <- function(percen){
  averagesampletrain=c()
  averagesampletest=c()
  for(i in 1:10){
  smp_size <- floor(percen * nrow(df_numeric))
  set.seed(123)
  #split data into train and test data
  spl <- sample(1:nrow(df_numeric), size = smp_size)
  sampledatatrain <- df_numeric[spl, ]
  sampledatatest <- df_numeric[-spl, ]
  #building linear regression model based on train data
  M1=lm(Gross~Year+Runtime+Metascore+imdbRating+imdbVotes+tomatoMeter+tomatoRating+tomatoReviews+tomatoFresh+tomatoUserMeter+tomatoUserRating+tomatoUserReviews+Budget,sampledatatrain)
  #obtain test set predictions from M1
  preTest=predict(M1, sampledatatest)
  preTest=as.data.frame(preTest)
  RSME_test=sqrt(mean((sampledatatest$Gross-preTest)^2))
  averagesampletrain=c(averagesampletrain,sqrt(residuals(M1)^2))
  averagesampletest=c(averagesampletest,RSME_test)
  }
  final=c()
  final=c(final,mean(averagesampletrain))
  final=c(final,mean(averagesampletest))
  return (final)
}
size <- c(0.05, 0.1, 0.15,0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95)
trainRSME=c(getaverageRMSE(0.05)[1],getaverageRMSE(0.1)[1],getaverageRMSE(0.15)[1],getaverageRMSE(0.2)[1],getaverageRMSE(0.25)[1],getaverageRMSE(0.3)[1],getaverageRMSE(0.35)[1],getaverageRMSE(0.4)[1],getaverageRMSE(0.45)[1],getaverageRMSE(0.5)[1],getaverageRMSE(0.55)[1],getaverageRMSE(0.6)[1],getaverageRMSE(0.65)[1],getaverageRMSE(0.7)[1],getaverageRMSE(0.75)[1],getaverageRMSE(0.8)[1],getaverageRMSE(0.85)[1],getaverageRMSE(0.9)[1],getaverageRMSE(0.95)[1])
testRSME=c(getaverageRMSE(0.05)[2],getaverageRMSE(0.1)[2],getaverageRMSE(0.15)[2],getaverageRMSE(0.2)[2],getaverageRMSE(0.25)[2],getaverageRMSE(0.3)[2],getaverageRMSE(0.35)[2],getaverageRMSE(0.4)[2],getaverageRMSE(0.45)[2],getaverageRMSE(0.5)[2],getaverageRMSE(0.55)[2],getaverageRMSE(0.6)[2],getaverageRMSE(0.65)[2],getaverageRMSE(0.7)[2],getaverageRMSE(0.75)[2],getaverageRMSE(0.8)[2],getaverageRMSE(0.85)[2],getaverageRMSE(0.9)[2],getaverageRMSE(0.95)[2])
dataformodel1<- data.frame(size, trainRSME,testRSME)
#Generate a graph of the averaged train and test RMSE as a function of the train set size (%)
ggplot(dataformodel1, aes(size)) + 
  geom_line(aes(y = trainRSME, color="train")) + 
  geom_line(aes(y = testRSME, color="test"))
```

**Q**: List all the numeric variables you used.

**A**: I used the following numeric variables: Year+Runtime+Metascore+imdbRating+imdbVotes+tomatoMeter+tomatoRating+tomatoReviews+tomatoFresh+tomatoUserMeter+tomatoUserRating+tomatoUserReviews+Budget

## 2. Feature transformations

Try to improve the prediction quality from **Task 1** as much as possible by adding feature transformations of the numeric variables. Explore both numeric transformations such as power transforms and non-numeric transformations of the numeric variables like binning (e.g. `is_budget_greater_than_3M`).

```{r}
# Build & evaluate model 2 (transformed numeric variables only)
#Budget
ggplot(df_numeric, aes(x=Budget^1.4, y=Gross)) +
    geom_point(shape=1) +    
    geom_smooth()
df_numeric$Budget <- df_numeric$Budget^1.4
trainRSME=c(getaverageRMSE(0.05)[1],getaverageRMSE(0.1)[1],getaverageRMSE(0.15)[1],getaverageRMSE(0.2)[1],getaverageRMSE(0.25)[1],getaverageRMSE(0.3)[1],getaverageRMSE(0.35)[1],getaverageRMSE(0.4)[1],getaverageRMSE(0.45)[1],getaverageRMSE(0.5)[1],getaverageRMSE(0.55)[1],getaverageRMSE(0.6)[1],getaverageRMSE(0.65)[1],getaverageRMSE(0.7)[1],getaverageRMSE(0.75)[1],getaverageRMSE(0.8)[1],getaverageRMSE(0.85)[1],getaverageRMSE(0.9)[1],getaverageRMSE(0.95)[1])
testRSME=c(getaverageRMSE(0.05)[2],getaverageRMSE(0.1)[2],getaverageRMSE(0.15)[2],getaverageRMSE(0.2)[2],getaverageRMSE(0.25)[2],getaverageRMSE(0.3)[2],getaverageRMSE(0.35)[2],getaverageRMSE(0.4)[2],getaverageRMSE(0.45)[2],getaverageRMSE(0.5)[2],getaverageRMSE(0.55)[2],getaverageRMSE(0.6)[2],getaverageRMSE(0.65)[2],getaverageRMSE(0.7)[2],getaverageRMSE(0.75)[2],getaverageRMSE(0.8)[2],getaverageRMSE(0.85)[2],getaverageRMSE(0.9)[2],getaverageRMSE(0.95)[2])
dataformodel2_1<- data.frame(size, trainRSME,testRSME)
#imdbVotes
ggplot(df_numeric, aes(x=imdbVotes^0.8, y=Gross)) +
    geom_point(shape=1) +    
    geom_smooth()
df_numeric$imdbVotes <- df_numeric$imdbVotes^0.8
trainRSME=c(getaverageRMSE(0.05)[1],getaverageRMSE(0.1)[1],getaverageRMSE(0.15)[1],getaverageRMSE(0.2)[1],getaverageRMSE(0.25)[1],getaverageRMSE(0.3)[1],getaverageRMSE(0.35)[1],getaverageRMSE(0.4)[1],getaverageRMSE(0.45)[1],getaverageRMSE(0.5)[1],getaverageRMSE(0.55)[1],getaverageRMSE(0.6)[1],getaverageRMSE(0.65)[1],getaverageRMSE(0.7)[1],getaverageRMSE(0.75)[1],getaverageRMSE(0.8)[1],getaverageRMSE(0.85)[1],getaverageRMSE(0.9)[1],getaverageRMSE(0.95)[1])
testRSME=c(getaverageRMSE(0.05)[2],getaverageRMSE(0.1)[2],getaverageRMSE(0.15)[2],getaverageRMSE(0.2)[2],getaverageRMSE(0.25)[2],getaverageRMSE(0.3)[2],getaverageRMSE(0.35)[2],getaverageRMSE(0.4)[2],getaverageRMSE(0.45)[2],getaverageRMSE(0.5)[2],getaverageRMSE(0.55)[2],getaverageRMSE(0.6)[2],getaverageRMSE(0.65)[2],getaverageRMSE(0.7)[2],getaverageRMSE(0.75)[2],getaverageRMSE(0.8)[2],getaverageRMSE(0.85)[2],getaverageRMSE(0.9)[2],getaverageRMSE(0.95)[2])
dataformodel2_2<- data.frame(size, trainRSME,testRSME)
#Runtime
ggplot(df_numeric, aes(x=Runtime, y=Gross)) +
    geom_point(shape=1) +    
    geom_smooth()
summary(df_numeric$Runtime)
df_numeric$Runtime<-cut(df_numeric$Runtime, seq(58,220,27), right=FALSE, labels=c(1:6))
trainRSME=c(getaverageRMSE(0.05)[1],getaverageRMSE(0.1)[1],getaverageRMSE(0.15)[1],getaverageRMSE(0.2)[1],getaverageRMSE(0.25)[1],getaverageRMSE(0.3)[1],getaverageRMSE(0.35)[1],getaverageRMSE(0.4)[1],getaverageRMSE(0.45)[1],getaverageRMSE(0.5)[1],getaverageRMSE(0.55)[1],getaverageRMSE(0.6)[1],getaverageRMSE(0.65)[1],getaverageRMSE(0.7)[1],getaverageRMSE(0.75)[1],getaverageRMSE(0.8)[1],getaverageRMSE(0.85)[1],getaverageRMSE(0.9)[1],getaverageRMSE(0.95)[1])
testRSME=c(getaverageRMSE(0.05)[2],getaverageRMSE(0.1)[2],getaverageRMSE(0.15)[2],getaverageRMSE(0.2)[2],getaverageRMSE(0.25)[2],getaverageRMSE(0.3)[2],getaverageRMSE(0.35)[2],getaverageRMSE(0.4)[2],getaverageRMSE(0.45)[2],getaverageRMSE(0.5)[2],getaverageRMSE(0.55)[2],getaverageRMSE(0.6)[2],getaverageRMSE(0.65)[2],getaverageRMSE(0.7)[2],getaverageRMSE(0.75)[2],getaverageRMSE(0.8)[2],getaverageRMSE(0.85)[2],getaverageRMSE(0.9)[2],getaverageRMSE(0.95)[2])
dataformodel2_3<- data.frame(size, trainRSME,testRSME)
#Metascore, no help in reducing RMSE while bining Metacore.
#imdbRating
ggplot(df_numeric, aes(x=imdbRating, y=Gross)) +
    geom_point(shape=1) +    
    geom_smooth()
summary(df_numeric$imdbRating)
df_numeric$imdbRatingoriginal <- df_numeric$imdbRating
df_numeric$imdbRating<-cut(df_numeric$imdbRating, seq(1.5,9.3,1.3), right=FALSE, labels=c(1:6))
trainRSME=c(getaverageRMSE(0.05)[1],getaverageRMSE(0.1)[1],getaverageRMSE(0.15)[1],getaverageRMSE(0.2)[1],getaverageRMSE(0.25)[1],getaverageRMSE(0.3)[1],getaverageRMSE(0.35)[1],getaverageRMSE(0.4)[1],getaverageRMSE(0.45)[1],getaverageRMSE(0.5)[1],getaverageRMSE(0.55)[1],getaverageRMSE(0.6)[1],getaverageRMSE(0.65)[1],getaverageRMSE(0.7)[1],getaverageRMSE(0.75)[1],getaverageRMSE(0.8)[1],getaverageRMSE(0.85)[1],getaverageRMSE(0.9)[1],getaverageRMSE(0.95)[1])
testRSME=c(getaverageRMSE(0.05)[2],getaverageRMSE(0.1)[2],getaverageRMSE(0.15)[2],getaverageRMSE(0.2)[2],getaverageRMSE(0.25)[2],getaverageRMSE(0.3)[2],getaverageRMSE(0.35)[2],getaverageRMSE(0.4)[2],getaverageRMSE(0.45)[2],getaverageRMSE(0.5)[2],getaverageRMSE(0.55)[2],getaverageRMSE(0.6)[2],getaverageRMSE(0.65)[2],getaverageRMSE(0.7)[2],getaverageRMSE(0.75)[2],getaverageRMSE(0.8)[2],getaverageRMSE(0.85)[2],getaverageRMSE(0.9)[2],getaverageRMSE(0.95)[2])
dataformodel2_4<- data.frame(size, trainRSME,testRSME)
df_numeric <- subset(df_numeric, select = -imdbRatingoriginal)
#tomatoMeter, no help in reducing RMSE while bining tomatoMeter.
#tomatoRating, no help in reducing RMSE while bining tomatoRating.
#tomatoReviews
ggplot(df_numeric, aes(x=tomatoReviews, y=Gross)) +
    geom_point(shape=1) +    
    geom_smooth()
summary(df_numeric$tomatoReviews)
df_numeric$tomatoReviewsoriginal <- df_numeric$tomatoReviews
df_numeric$tomatoReviews<-cut(df_numeric$tomatoReviews, seq(5.0,356.0,58.5), right=FALSE, labels=c(1:6))
trainRSME=c(getaverageRMSE(0.05)[1],getaverageRMSE(0.1)[1],getaverageRMSE(0.15)[1],getaverageRMSE(0.2)[1],getaverageRMSE(0.25)[1],getaverageRMSE(0.3)[1],getaverageRMSE(0.35)[1],getaverageRMSE(0.4)[1],getaverageRMSE(0.45)[1],getaverageRMSE(0.5)[1],getaverageRMSE(0.55)[1],getaverageRMSE(0.6)[1],getaverageRMSE(0.65)[1],getaverageRMSE(0.7)[1],getaverageRMSE(0.75)[1],getaverageRMSE(0.8)[1],getaverageRMSE(0.85)[1],getaverageRMSE(0.9)[1],getaverageRMSE(0.95)[1])
testRSME=c(getaverageRMSE(0.05)[2],getaverageRMSE(0.1)[2],getaverageRMSE(0.15)[2],getaverageRMSE(0.2)[2],getaverageRMSE(0.25)[2],getaverageRMSE(0.3)[2],getaverageRMSE(0.35)[2],getaverageRMSE(0.4)[2],getaverageRMSE(0.45)[2],getaverageRMSE(0.5)[2],getaverageRMSE(0.55)[2],getaverageRMSE(0.6)[2],getaverageRMSE(0.65)[2],getaverageRMSE(0.7)[2],getaverageRMSE(0.75)[2],getaverageRMSE(0.8)[2],getaverageRMSE(0.85)[2],getaverageRMSE(0.9)[2],getaverageRMSE(0.95)[2])
dataformodel2_5<- data.frame(size, trainRSME,testRSME)
df_numeric <- subset(df_numeric, select = -tomatoReviewsoriginal)
#tomatoFresh
ggplot(df_numeric, aes(x=tomatoFresh, y=Gross)) +
    geom_point(shape=1) +    
    geom_smooth()
summary(df_numeric$tomatoFresh)
df_numeric$tomatoFreshoriginal <- df_numeric$tomatoFresh
df_numeric$tomatoFresh <- df_numeric$tomatoFreshoriginal
df_numeric$tomatoFresh<-cut(df_numeric$tomatoFresh, seq(0,345.0,115), right=FALSE, labels=c(1:3))
trainRSME=c(getaverageRMSE(0.05)[1],getaverageRMSE(0.1)[1],getaverageRMSE(0.15)[1],getaverageRMSE(0.2)[1],getaverageRMSE(0.25)[1],getaverageRMSE(0.3)[1],getaverageRMSE(0.35)[1],getaverageRMSE(0.4)[1],getaverageRMSE(0.45)[1],getaverageRMSE(0.5)[1],getaverageRMSE(0.55)[1],getaverageRMSE(0.6)[1],getaverageRMSE(0.65)[1],getaverageRMSE(0.7)[1],getaverageRMSE(0.75)[1],getaverageRMSE(0.8)[1],getaverageRMSE(0.85)[1],getaverageRMSE(0.9)[1],getaverageRMSE(0.95)[1])
testRSME=c(getaverageRMSE(0.05)[2],getaverageRMSE(0.1)[2],getaverageRMSE(0.15)[2],getaverageRMSE(0.2)[2],getaverageRMSE(0.25)[2],getaverageRMSE(0.3)[2],getaverageRMSE(0.35)[2],getaverageRMSE(0.4)[2],getaverageRMSE(0.45)[2],getaverageRMSE(0.5)[2],getaverageRMSE(0.55)[2],getaverageRMSE(0.6)[2],getaverageRMSE(0.65)[2],getaverageRMSE(0.7)[2],getaverageRMSE(0.75)[2],getaverageRMSE(0.8)[2],getaverageRMSE(0.85)[2],getaverageRMSE(0.9)[2],getaverageRMSE(0.95)[2])
dataformodel2_6<- data.frame(size, trainRSME,testRSME)
df_numeric <- subset(df_numeric, select = -tomatoFreshoriginal)
#tomatoUserMeter, no help in reducing RMSE while bining tomatoUserMeter.
#tomatoUserRating
ggplot(df_numeric, aes(x=tomatoUserRating, y=Gross)) +
    geom_point(shape=1) +    
    geom_smooth()
summary(df_numeric$tomatoUserRating)
df_numeric$tomatoUserRatingoriginal <- df_numeric$tomatoUserRating
df_numeric$tomatoUserRating <- df_numeric$tomatoUserRatingoriginal
df_numeric$tomatoUserRating<-cut(df_numeric$tomatoUserRating, seq(1.5,4.8,0.825), right=FALSE, labels=c(1:4))
trainRSME=c(getaverageRMSE(0.05)[1],getaverageRMSE(0.1)[1],getaverageRMSE(0.15)[1],getaverageRMSE(0.2)[1],getaverageRMSE(0.25)[1],getaverageRMSE(0.3)[1],getaverageRMSE(0.35)[1],getaverageRMSE(0.4)[1],getaverageRMSE(0.45)[1],getaverageRMSE(0.5)[1],getaverageRMSE(0.55)[1],getaverageRMSE(0.6)[1],getaverageRMSE(0.65)[1],getaverageRMSE(0.7)[1],getaverageRMSE(0.75)[1],getaverageRMSE(0.8)[1],getaverageRMSE(0.85)[1],getaverageRMSE(0.9)[1],getaverageRMSE(0.95)[1])
testRSME=c(getaverageRMSE(0.05)[2],getaverageRMSE(0.1)[2],getaverageRMSE(0.15)[2],getaverageRMSE(0.2)[2],getaverageRMSE(0.25)[2],getaverageRMSE(0.3)[2],getaverageRMSE(0.35)[2],getaverageRMSE(0.4)[2],getaverageRMSE(0.45)[2],getaverageRMSE(0.5)[2],getaverageRMSE(0.55)[2],getaverageRMSE(0.6)[2],getaverageRMSE(0.65)[2],getaverageRMSE(0.7)[2],getaverageRMSE(0.75)[2],getaverageRMSE(0.8)[2],getaverageRMSE(0.85)[2],getaverageRMSE(0.9)[2],getaverageRMSE(0.95)[2])
dataformodel2_7<- data.frame(size, trainRSME,testRSME)
df_numeric <- subset(df_numeric, select = -tomatoUserRatingoriginal)
#tomatoUserReviews, no help in reducing RMSE while bining tomatoUserReviews.

#Generate a graph of the averaged train and test RMSE as a function of the train set size (%)
ggplot(dataformodel2_7, aes(size)) + 
  geom_line(aes(y = trainRSME, color="train")) + 
  geom_line(aes(y = testRSME, color="test"))
```

**Q**: Explain which transformations you used and why you chose them.

**A**: 
As shown from scatter plots, I decided to do power transformation for Budget and imdbVotes, and do bining for other variables.
1. Budget was transformed into Budget^1.4.After changing the variables bit by bit (0.5,1.5,2) and checking on the RMSEs, 1.5 works best, therefore I changed it to 1.4 and 1.6 and checked the RMSEs. Eventually, I decided to use 1.4. This process was carried out with imdbVotes and it was transformed into imdbVotes^0.8.
2. I tried bining for the rest varibales and checked the RMSEs, eventually, I decided to bin tomatoUserRating, tomatoFresh, tomatoReviews, imdbRating, and Runtime.
Overall, when the training data is 0.95,RSME in test data jumped from 77770187 to 69955011.

## 3. Non-numeric variables

Write code that converts genre, actors, directors, and other categorical variables to columns that can be used for regression (e.g. binary columns as you did in Project 1). Also process variables such as awards into more useful columns (again, like you did in Project 1). Now use these converted columns only to build your next model.

```{r}
# Build & evaluate model 3 (converted non-numeric variables only)
#whether it's an comedy movive or not
pattern <- "Comedy|comedy"
df_numeric$comedy <- grepl(pattern, df_numeric$Genre)
df_numeric$comedy <- 1*df_numeric$comedy
#number of nominations 
nominations=sapply(df_numeric$Awards, function(x) regmatches(x,gregexpr("(ominated\\sfor\\s[0-9]+)|([0-9]+\\snomination)",x))[[1]])
nominations=sapply(nominations, function(x) sum(as.numeric(unlist(regmatches(x,gregexpr("[0-9]+",x))))))
df_numeric$nominations=nominations
getaverageRMSE <- function(percen){
  averagesampletrain=c()
  averagesampletest=c()
  for(i in 1:10){
  smp_size <- floor(percen * nrow(df_numeric))
  set.seed(123)
  #split data into train and test data
  spl <- sample(1:nrow(df_numeric), size = smp_size)
  sampledatatrain <- df_numeric[spl, ]
  sampledatatest <- df_numeric[-spl, ]
  #building linear regression model based on train data
  M1=lm(Gross~comedy+nominations,sampledatatrain)
  #obtain test set predictions from M1
  preTest=predict(M1, sampledatatest)
  preTest=as.data.frame(preTest)
  RSME_test=sqrt(mean((sampledatatest$Gross-preTest)^2))
  averagesampletrain=c(averagesampletrain,sqrt(residuals(M1)^2))
  averagesampletest=c(averagesampletest,RSME_test)
  }
  final=c()
  final=c(final,mean(averagesampletrain))
  final=c(final,mean(averagesampletest))
  return (final)
}
trainRSME=c(getaverageRMSE(0.05)[1],getaverageRMSE(0.1)[1],getaverageRMSE(0.15)[1],getaverageRMSE(0.2)[1],getaverageRMSE(0.25)[1],getaverageRMSE(0.3)[1],getaverageRMSE(0.35)[1],getaverageRMSE(0.4)[1],getaverageRMSE(0.45)[1],getaverageRMSE(0.5)[1],getaverageRMSE(0.55)[1],getaverageRMSE(0.6)[1],getaverageRMSE(0.65)[1],getaverageRMSE(0.7)[1],getaverageRMSE(0.75)[1],getaverageRMSE(0.8)[1],getaverageRMSE(0.85)[1],getaverageRMSE(0.9)[1],getaverageRMSE(0.95)[1])
testRSME=c(getaverageRMSE(0.05)[2],getaverageRMSE(0.1)[2],getaverageRMSE(0.15)[2],getaverageRMSE(0.2)[2],getaverageRMSE(0.25)[2],getaverageRMSE(0.3)[2],getaverageRMSE(0.35)[2],getaverageRMSE(0.4)[2],getaverageRMSE(0.45)[2],getaverageRMSE(0.5)[2],getaverageRMSE(0.55)[2],getaverageRMSE(0.6)[2],getaverageRMSE(0.65)[2],getaverageRMSE(0.7)[2],getaverageRMSE(0.75)[2],getaverageRMSE(0.8)[2],getaverageRMSE(0.85)[2],getaverageRMSE(0.9)[2],getaverageRMSE(0.95)[2])
dataformodel3_1<- data.frame(size, trainRSME,testRSME)
#Generate a graph of the averaged train and test RMSE as a function of the train set size (%)
ggplot(dataformodel3_1, aes(size)) + 
  geom_line(aes(y = trainRSME, color="train")) + 
  geom_line(aes(y = testRSME, color="test"))
```

**Q**: Explain which categorical variables you used, and how you encoded them into features.

**A**: I used two categorical variables: whether the movie is comedy or not, and how many nominations the movie got. I searched online and got the sense that comedy movies have more gross. Thus, I encoded comedy movies into 1 and others to be 0. I used number of nominations, instead of number of awards because it captures more of the audiences' taste. 

## 4. Numeric and categorical variables

Try to improve the prediction quality as much as possible by using both numeric and non-numeric variables from **Tasks 2 & 3**.

```{r}
# Build & evaluate model 4 (numeric & converted non-numeric variables)
#combine 2 and 3
getaverageRMSE <- function(percen){
  averagesampletrain=c()
  averagesampletest=c()
  for(i in 1:10){
  smp_size <- floor(percen * nrow(df_numeric))
  set.seed(123)
  #split data into train and test data
  spl <- sample(1:nrow(df_numeric), size = smp_size)
  sampledatatrain <- df_numeric[spl, ]
  sampledatatest <- df_numeric[-spl, ]
  #building linear regression model based on train data
  M1=lm(Gross~Year+Runtime+Metascore+imdbRating+imdbVotes+tomatoMeter+tomatoRating+tomatoReviews+tomatoFresh+tomatoUserMeter+tomatoUserRating+tomatoUserReviews+Budget+comedy+nominations,sampledatatrain)
  #obtain test set predictions from M1
  preTest=predict(M1, sampledatatest)
  preTest=as.data.frame(preTest)
  RSME_test=sqrt(mean((sampledatatest$Gross-preTest)^2))
  averagesampletrain=c(averagesampletrain,sqrt(residuals(M1)^2))
  averagesampletest=c(averagesampletest,RSME_test)
  }
  final=c()
  final=c(final,mean(averagesampletrain))
  final=c(final,mean(averagesampletest))
  return (final)
}
trainRSME=c(getaverageRMSE(0.05)[1],getaverageRMSE(0.1)[1],getaverageRMSE(0.15)[1],getaverageRMSE(0.2)[1],getaverageRMSE(0.25)[1],getaverageRMSE(0.3)[1],getaverageRMSE(0.35)[1],getaverageRMSE(0.4)[1],getaverageRMSE(0.45)[1],getaverageRMSE(0.5)[1],getaverageRMSE(0.55)[1],getaverageRMSE(0.6)[1],getaverageRMSE(0.65)[1],getaverageRMSE(0.7)[1],getaverageRMSE(0.75)[1],getaverageRMSE(0.8)[1],getaverageRMSE(0.85)[1],getaverageRMSE(0.9)[1],getaverageRMSE(0.95)[1])
testRSME=c(getaverageRMSE(0.05)[2],getaverageRMSE(0.1)[2],getaverageRMSE(0.15)[2],getaverageRMSE(0.2)[2],getaverageRMSE(0.25)[2],getaverageRMSE(0.3)[2],getaverageRMSE(0.35)[2],getaverageRMSE(0.4)[2],getaverageRMSE(0.45)[2],getaverageRMSE(0.5)[2],getaverageRMSE(0.55)[2],getaverageRMSE(0.6)[2],getaverageRMSE(0.65)[2],getaverageRMSE(0.7)[2],getaverageRMSE(0.75)[2],getaverageRMSE(0.8)[2],getaverageRMSE(0.85)[2],getaverageRMSE(0.9)[2],getaverageRMSE(0.95)[2])
dataformodel4_1<- data.frame(size, trainRSME,testRSME)
#Generate a graph of the averaged train and test RMSE as a function of the train set size (%)
ggplot(dataformodel4_1, aes(size)) + 
  geom_line(aes(y = trainRSME, color="train")) + 
  geom_line(aes(y = testRSME, color="test"))
```

## 5. Additional features

Now try creating additional features such as interactions (e.g. `is_genre_comedy` x `is_budget_greater_than_3M`) or deeper analysis of complex variables (e.g. text analysis of full-text columns like `Plot`).

```{r}
# Build & evaluate model 5 (numeric, non-numeric and additional features)
summary(df_numeric$Budget)
df_numeric$bugetgreaterthan3 = ifelse(df_numeric$Budget > (3000000^1.4), 1, 0)
df_numeric$interaction = df_numeric$bugetgreaterthan3* df_numeric$comedy
getaverageRMSE <- function(percen){
  averagesampletrain=c()
  averagesampletest=c()
  for(i in 1:10){
  smp_size <- floor(percen * nrow(df_numeric))
  set.seed(123)
  #split data into train and test data
  spl <- sample(1:nrow(df_numeric), size = smp_size)
  sampledatatrain <- df_numeric[spl, ]
  sampledatatest <- df_numeric[-spl, ]
  #building linear regression model based on train data
  M1=lm(Gross~Year+Runtime+Metascore+imdbRating+imdbVotes+tomatoMeter+tomatoRating+tomatoReviews+tomatoFresh+tomatoUserMeter+tomatoUserRating+tomatoUserReviews+Budget+comedy+nominations+interaction,sampledatatrain)
  #obtain test set predictions from M1
  preTest=predict(M1, sampledatatest)
  preTest=as.data.frame(preTest)
  RSME_test=sqrt(mean((sampledatatest$Gross-preTest)^2))
  averagesampletrain=c(averagesampletrain,sqrt(residuals(M1)^2))
  averagesampletest=c(averagesampletest,RSME_test)
  }
  final=c()
  final=c(final,mean(averagesampletrain))
  final=c(final,mean(averagesampletest))
  return (final)
}
trainRSME=c(getaverageRMSE(0.05)[1],getaverageRMSE(0.1)[1],getaverageRMSE(0.15)[1],getaverageRMSE(0.2)[1],getaverageRMSE(0.25)[1],getaverageRMSE(0.3)[1],getaverageRMSE(0.35)[1],getaverageRMSE(0.4)[1],getaverageRMSE(0.45)[1],getaverageRMSE(0.5)[1],getaverageRMSE(0.55)[1],getaverageRMSE(0.6)[1],getaverageRMSE(0.65)[1],getaverageRMSE(0.7)[1],getaverageRMSE(0.75)[1],getaverageRMSE(0.8)[1],getaverageRMSE(0.85)[1],getaverageRMSE(0.9)[1],getaverageRMSE(0.95)[1])
testRSME=c(getaverageRMSE(0.05)[2],getaverageRMSE(0.1)[2],getaverageRMSE(0.15)[2],getaverageRMSE(0.2)[2],getaverageRMSE(0.25)[2],getaverageRMSE(0.3)[2],getaverageRMSE(0.35)[2],getaverageRMSE(0.4)[2],getaverageRMSE(0.45)[2],getaverageRMSE(0.5)[2],getaverageRMSE(0.55)[2],getaverageRMSE(0.6)[2],getaverageRMSE(0.65)[2],getaverageRMSE(0.7)[2],getaverageRMSE(0.75)[2],getaverageRMSE(0.8)[2],getaverageRMSE(0.85)[2],getaverageRMSE(0.9)[2],getaverageRMSE(0.95)[2])
dataformodel5_1<- data.frame(size, trainRSME,testRSME)
#Generate a graph of the averaged train and test RMSE as a function of the train set size (%)
ggplot(dataformodel5_1, aes(size)) + 
  geom_line(aes(y = trainRSME, color="train")) + 
  geom_line(aes(y = testRSME, color="test"))
#generate a graph of all final models
dataformodel <- merge(dataformodel1, dataformodel2_7,by="size")
dataformodel <- merge(dataformodel, dataformodel3_1,by="size")
dataformodel <- merge(dataformodel, dataformodel4_1, by="size")
dataformodel <- merge(dataformodel, dataformodel5_1, by="size")
colnames(dataformodel) <- c("size", "model1_train","model1_test","model2_train","model2_test","model3_train","model3_test","model4_train","model4_test","model5_train","model5_test")
#compare test RMSEs in five models
ggplot(dataformodel, aes(size)) + 
  geom_line(aes(y = model1_test, color="model1_test")) + 
  geom_line(aes(y = model2_test, color="model2_test"))+ 
  geom_line(aes(y = model3_test, color="model3_test"))+ 
  geom_line(aes(y = model4_test, color="model4_test"))+ 
  geom_line(aes(y = model5_test, color="model5_test"))
#compare train RMSEs in five models
ggplot(dataformodel, aes(size)) + 
  geom_line(aes(y = model1_train, color="model1_train")) + 
  geom_line(aes(y = model2_train, color="model2_train"))+ 
  geom_line(aes(y = model3_train, color="model3_train"))+ 
  geom_line(aes(y = model4_train, color="model4_train"))+ 
  geom_line(aes(y = model5_train, color="model5_train"))
```

**Q**: Explain what new features you designed and why you chose them.

**A**: I used interactions between "whether the movie is comedy or not" with "whether budget is greater than 3M or not" bacause my assumption is that gross will be larger if a comedy cost more.In addition, i compared five models. The model was improved slightly.
