# Data

In this project, you will explore a dataset that contains information about movies, including ratings, budget, gross revenue and other attributes. It was prepared by Dr. Guy Lebanon, and here is his description of the dataset:

> The file [`movies_merged`](https://s3.amazonaws.com/content.udacity-data.com/courses/gt-cs6242/project/movies_merged) contains a dataframe with the same name that has 40K rows and 39 columns. Each row represents a movie title and each column represents a descriptor such as `Title`, `Actors`, and `Budget`. I collected the data by querying IMDb’s API (see [www.omdbapi.com](http://www.omdbapi.com/)) and joining it with a separate dataset of movie budgets and gross earnings (unknown to you). The join key was the movie title. This data is available for personal use, but IMDb’s terms of service do not allow it to be used for commercial purposes or for creating a competing repository.

# Objective

Your goal is to investigate the relationship between the movie descriptors and the box office success of movies, as represented by the variable `Gross`. This task is extremely important as it can help a studio decide which titles to fund for production, how much to bid on produced movies, when to release a title, how much to invest in marketing and PR, etc. This information is most useful before a title is released, but it is still very valuable after the movie is already released to the public (for example it can affect additional marketing spend or how much a studio should negotiate with on-demand streaming companies for “second window” streaming rights).

# Setup

## Load data

Make sure you've downloaded the [`movies_merged`](https://s3.amazonaws.com/content.udacity-data.com/courses/gt-cs6242/project/movies_merged) file and it is in the current working directory. Now load it into memory:

```{r}
load('movies_merged')
```

This creates an object of the same name (`movies_merged`). For convenience, you can copy it to `df` and start using it:

```{r}
df = movies_merged
cat("Dataset has", dim(df)[1], "rows and", dim(df)[2], "columns", end="\n", file="")
colnames(df)
```

## Load R packages

Load any R packages that you will need to use. You can come back to this chunk, edit it and re-run to load any additional packages later.

```{r}
library(ggplot2)
library(GGally)
library(NLP)
library(tm)
library(stringr)
library(tidyr)
```

If you are loading any non-standard packages (ones that have not been discussed in class or explicitly allowed for this project), please mention them below. Include any special instructions if they cannot be installed using the regular `install.packages('<pkg name>')` command.

**Non-standard packages used**: None

# Tasks

Each task below is worth **10** points, and is meant to be performed sequentially, i.e. do step 2 after you have processed the data as described in step 1. Total points: **100**

Complete each task by implementing code chunks as described by `TODO` comments, and by responding to questions ("**Q**:") with written answers ("**A**:"). If you are unable to find a meaningful or strong relationship in any of the cases when requested, explain why not by referring to appropriate plots/statistics.

It is OK to handle missing values below by omission, but please omit as little as possible. It is worthwhile to invest in reusable and clear code as you may need to use it or modify it in project 2.

## 1. Remove non-movie rows

The variable `Type` captures whether the row is a movie, a TV series, or a game. Remove all rows from `df` that do not correspond to movies.

```{r}
# TODO: Remove all rows from df that do not correspond to movies
df=df[df$Type=="movie", ]
print(dim(df)[1])
```


**Q**: How many rows are left after removal? _Enter your response below._

**A**:40000 rows are left

## 2. Process `Runtime` column

The variable `Runtime` represents the length of the title as a string. Write R code to convert it to a numeric value (in minutes) and replace `df$Runtime` with the new numeric column.

```{r}
# TODO: Replace df$Runtime with a numeric column containing the runtime in minutes
df$Runtime[df$Runtime=="1 h"] <- "60 min"#change runtime 1 h to be 60 min
df=df[df$Runtime!="N/A",]#remove columns without runtime
df$newtime <- str_extract_all(df$Runtime,"\\(?[0-9,.]+\\)?",simplify = TRUE)#extract runtime as seperate numbers
newpairs <- matrix(df$newtime, ncol=2)
df$hour <- as.numeric(newpairs[,1])
df$minute <- as.numeric(newpairs[,2])
df$finaltime <- ifelse(!(is.na(df$minute)),df$hour*60+df$minute, df$hour) #if there are two numbers in the newtime, then first*60+second, or else keep the same
df$Runtime <- df$finaltime#replace runtime with finaltime
```

Now investigate the distribution of `Runtime` values and how it changes over years (variable `Year`, which you can bucket into decades) and in relation to the budget (variable `Budget`). Include any plots that illustrate.

```{r}
# TODO: Investigate the distribution of Runtime values and how it varies by Year and Budget
ggplot(data=df, aes(df$Runtime))+geom_histogram()
summary(df$Runtime)
ggplot(df, aes(x=df$Year, y=df$Runtime))+geom_point()
ggplot(df, aes(x=Budget, y=Runtime)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
summary(df$Year)#min: 1888, max: 2018, median: 1989, mean:1981
df$ColorYear[df$Year>=1888&df$Year<=1970]="1888-1970"
df$ColorYear[df$Year>=1970&df$Year<=1980]="1970-1980"
df$ColorYear[df$Year>=1980&df$Year<=1990]="1980-1990"
df$ColorYear[df$Year>=1990&df$Year<=2000]="1990-2000"
df$ColorYear[df$Year>2000&df$Year<=2010]="2000-2010"
df$ColorYear[df$Year>2010&df$Year<=2018]="2010-2018"
p<-ggplot(df, aes(x=Budget, y=Runtime)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
p+facet_wrap(~ColorYear)
```

_Feel free to insert additional code chunks as necessary._

**Q**: Comment on the distribution as well as relationships. Are there any patterns or trends that you can observe?

**A**: The histogram shows that the majority of runtime was around 100 mins. Then, let's explore whether the runtime has any relationship with when the movie was made or the budget of the movie. Typically, line charts are suitable for showing trends (e.g., runtime over years). But there are lots of movies in one single year. Therefore, a scatter plot was created to show the relationship between runtime and year. The scatter plot shows that runtime was short before 1910 and it became more diverse afterward. After 1910, most movies are less than 250 mins, but a few outliers are much longer than 250 mins. As for the relationship between runtime and budget, initially, a scatter plot was created to explore the relationship. As the scatter plot shows, the runtime varies within one single budget. And the regression line did not show a clear trend. Therefore, there is no strong relationship between runtime and budget. But let's dig more into it and see whether there is any relationship for different time period. Therefore, I created separate scatter plots and regression lines for each time period (1888-1970, 1970-1980, 1980-1990, 1990-2000, 2000-2010, 2010-2018). During 1888-1970, the budget range was smaller and we can see a clear trend of "larger budget~longer runtime". During 1980-1990, sometimes shorter runtime could be associated with a larger budget. During other time periods, the trend is not strong, but we can still see a trend of "larger budget~longer runtime".

## 3. Encode `Genre` column

The column `Genre` represents a list of genres associated with the movie in a string format. Write code to parse each text string into a binary vector with 1s representing the presence of a genre and 0s the absence, and add it to the dataframe as additional columns. Then remove the original `Genre` column.

For example, if there are a total of 3 genres: Drama, Comedy, and Action, a movie that is both Action and Comedy should be represented by a binary vector <0, 1, 1>. Note that you need to first compile a dictionary of all possible genres and then figure out which movie has which genres (you can use the R `tm` package to create the dictionary).

```{r}
# TODO: Replace Genre with a collection of binary columns
myCorpus <- Corpus(VectorSource(df$Genre))
myTDM <- DocumentTermMatrix(myCorpus)
myTDMmatrix <- as.matrix(myTDM)
df$Genre <- myTDMmatrix #replace the column Genre
```

Plot the relative proportions of movies having the top 10 most common genres.

```{r}
# TODO: Select movies from top 10 most common genres and plot their relative proportions
# get top 10 generas
freq <- colSums(as.matrix(myTDM))
freq
ord <- order(freq, decreasing=TRUE)
ord[1:10]#order number of top N genres
freq[ord][1:10]
frematrix <- as.data.frame(freq[ord][1:10])#top 10 generas
colnames(frematrix)[1] <- "frequencygenre"
frematrix
frematrix$topgenre <- rownames(frematrix)
frematrix
#number of movies for each genre, note there are 39249 movies in total
frematrix$frequencygenre <- frematrix$frequencygenre/39249 #get the proportions for each genre
frematrix
ggplot(frematrix, aes(x=topgenre, y=frequencygenre))+geom_bar(stat ="identity")
```

Examine how the distribution of `Runtime` changes across genres for the top 10 most common genres.

```{r}
# TODO: Plot Runtime distribution for top 10 most common genres
subset1 <- subset(df, df$Genre[,6]==1)#1drama
subset2 <- subset(df, df$Genre[,8]==1)#2comedy
subset3 <- subset(df, df$Genre[,4]==1)#3short
subset4 <- subset(df, df$Genre[,3]==1)#4romance
subset5 <- subset(df, df$Genre[,15]==1)#5action
subset6 <- subset(df, df$Genre[,14]==1)#6crime
subset7 <- subset(df, df$Genre[,5]==1)#7thriller
subset8 <- subset(df, df$Genre[,2]==1)#8documentory
subset9 <- subset(df, df$Genre[,11]==1)#9adventure
subset10 <- subset(df, df$Genre[,20]==1)#10animation
attach(mtcars)
par(mfrow=c(5,2))
ggplot(data=subset1, aes(subset1$Runtime))+geom_histogram()
ggplot(data=subset2, aes(subset2$Runtime))+geom_histogram()
ggplot(data=subset3, aes(subset3$Runtime))+geom_histogram()
ggplot(data=subset4, aes(subset4$Runtime))+geom_histogram()
ggplot(data=subset5, aes(subset5$Runtime))+geom_histogram()
ggplot(data=subset6, aes(subset6$Runtime))+geom_histogram()
ggplot(data=subset7, aes(subset7$Runtime))+geom_histogram()
ggplot(data=subset8, aes(subset8$Runtime))+geom_histogram()
ggplot(data=subset9, aes(subset9$Runtime))+geom_histogram()
ggplot(data=subset10, aes(subset10$Runtime))+geom_histogram()
```

**Q**: Describe the interesting relationship(s) you observe. Are there any expected or unexpected trends that are evident?

**A**: Drama: median is 96 and mean is 96.94; Comedy: median is 90 and mean is 79; Short:median is 11 and mean is 13.92; Romance: median is 96 and mean is 98; Action: median is 95 and mean is 98.8; Crime: median is 95 and mean is 95.9; Thriller: median is 95 and mean is 96.4; Documentary: median is 73 and mean is 67.52; Adventure: median is 95 and mean is 99; Animation median is 7 and mean is 20.8. 1) Animation stood up for the fact that the mean was much greater than the median. The last histogram also showed a right skewed distribution. It represented that the runtime of most animations was short.  2) Histograms showed that the peak of the following genres is around 100 min: drama, comedy, romance, action, crime, thriller, and adventure. 3) Comedy stood up for the fact that the median was much greater than the mean. The histogram also showed a left skewed distribution.  One unexpected trend was that the animation is shorter than the short movie. 

## 4. Eliminate mismatched rows

The dataframe was put together by merging two different sources of data and it is possible that the merging process was inaccurate in some cases (the merge was done based on movie title, but there are cases of different movies with the same title). The first source’s release time was represented by the column `Year` (numeric representation of the year) and the second by the column `Released` (string representation of release date).

Find and remove all rows where you suspect a merge error occurred based on a mismatch between these two variables. To make sure subsequent analysis and modeling work well, avoid removing more than 10% of the rows that have a `Gross` value present.

```{r}
# TODO: Remove rows with Released-Year mismatch
countGross = sum(!is.na(df$Gross))#number of rows that has Gross value
countGross #4520 rows has gross value
limitation = countGross*0.1
limitation # avoid removing more than 452 rows
subsetmatch <- subset(df, as.numeric(substr(df$Released,1,4))-as.numeric(df$Year)<=1) # remaining 32768 rows
countGrossMatch = sum(!is.na(subsetmatch$Gross))
countGrossMatch #4397 has gross value, so there are 4520-4397 rows are deleted
```

**Q**: What is your precise removal logic and how many rows did you end up removing?

**A**: Firstly, in the df dataset, there are 4520 rows having gross value, therefore, I should avoid removing more than 452 rows. And then I created a subset out of df, it's called subsetmacth. If the difference between release year and year is less than one, then I will keep the row in the subsetmatch. Eventually, there are 32768 rows left. In addition, there are 4397 rows with the gross value in the subsetmatch. Therefore, 123 rows with gross value are removed, which is less than 452 rows. Therefore, the removing action meet the criteria.

## 5. Explore `Gross` revenue

For the commercial success of a movie, production houses want to maximize Gross revenue. Investigate if Gross revenue is related to Budget, Runtime or Genre in any way.

Note: To get a meaningful relationship, you may have to partition the movies into subsets such as short vs. long duration, or by genre, etc.

```{r}
# TODO: Investigate if Gross Revenue is related to Budget, Runtime or Genre
# gross vs budget
p<-ggplot(subsetmatch, aes(x=Budget, y=Gross)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
p
# gross vs runtime
p<-ggplot(subsetmatch, aes(x=Budget, y=Runtime)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
summary(subsetmatch$Runtime) # runtime: median 91.0; mean 84.3; max 873.0; min 1 min; 1st qu. 75.0; 3rd qu 102.0
subset75 <- subset(df, subsetmatch$Runtime<=75)#<75.0
subset102 <- subset(df, subsetmatch$Runtime>=75&subsetmatch$Runtime<=102)#>75.0 & <102
subset130 <- subset(df, subsetmatch$Runtime>=102&subsetmatch$Runtime<=130)#>102 & <130 
subsetlong <- subset(df, subsetmatch$Runtime>=130)#>130
attach(mtcars)
par(mfrow=c(2,2))
ggplot(subset75, aes(x=Budget, y=Runtime)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
ggplot(subset102, aes(x=Budget, y=Runtime)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
ggplot(subset130, aes(x=Budget, y=Runtime)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
ggplot(subsetlong, aes(x=Budget, y=Runtime)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
# gross vs runtime in top 10 genres
#here, I only talk about top 10 genres, instead of showing all 30 genres
attach(mtcars)
par(mfrow=c(5,2))
ggplot(subset1, aes(x=Runtime, y=Gross)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
ggplot(subset2, aes(x=Runtime, y=Gross)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
ggplot(subset3, aes(x=Runtime, y=Gross)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
ggplot(subset4, aes(x=Runtime, y=Gross)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
ggplot(subset5, aes(x=Runtime, y=Gross)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
ggplot(subset6, aes(x=Runtime, y=Gross)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
ggplot(subset7, aes(x=Runtime, y=Gross)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
ggplot(subset8, aes(x=Runtime, y=Gross)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
ggplot(subset9, aes(x=Runtime, y=Gross)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
ggplot(subset10, aes(x=Runtime, y=Gross)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
```

**Q**: Did you find any observable relationships or combinations of Budget/Runtime/Genre that result in high Gross revenue? If you divided the movies into different subsets, you may get different answers for them - point out interesting ones.

**A**: The regression line shows that higher budgets potentially offer higher gross. The regression line of "budget vs runtime" does not show a clear relationship between those two variables. But after dividing runtime as longer time and shorter time periods and then plot them out, the time period between 102 to 130 has a clearer relationship between runtime and gross. It shows that longer runtime has higher gross during the particular time period. While looking at regressions lines of "gross ~ runtime" in top 10 genres, some more interesting trends come out. For short movies, gross increases sharply as runtime increases. For drama, action, crime, thriller, documentary, adventure, and animation, there is a threshold of runtime. After a threshold, gross decreases as runtime increases. 

```{r}
# TODO: Investigate if Gross Revenue is related to Release Month
#create 2 dummy variables based on movie release date; one for Summer Release (movies that are released from May through August) and Christmas release (movies that are released in December). Based on our domain knowledge, we believe those two are the peak period where audiences go to the theater and big budget movies are released. 
#plot it out
subsetmatch$month <- as.numeric(substr(subsetmatch$Released, 6,7))#make a new column that holds the variable month
monthgrossnum <- aggregate(Gross~month,subsetmatch,length)
names(monthgrossnum)[2] <- 'num'
monthgrossnum
monthgrosssum <- aggregate(Gross~month,subsetmatch,sum)
names(monthgrosssum)[2] <- 'sum'
monthgrosssum
monthgross <- merge(monthgrossnum,monthgrosssum)
monthgross <- as.data.frame(monthgross) 
monthgross
monthgross$average <- monthgross$sum/monthgross$num #average gross for each month
ggplot(monthgross, aes(x=reorder(month, average), y=average))+geom_bar(stat="identity") # as you can see from the bar chart, 11, 7, 12, 6, 5 are the months that have high gross. It's a common sense because summer release and christmas release are peak periods whenaudience go to the theater.
```

## 6. Process `Awards` column

The variable `Awards` describes nominations and awards in text format. Convert it to 2 numeric columns, the first capturing the number of wins, and the second capturing nominations. Replace the `Awards` column with these new columns, and then study the relationship of `Gross` revenue with respect to them.

Note that the format of the `Awards` column is not standard; you may have to use regular expressions to find the relevant values. Try your best to process them, and you may leave the ones that don't have enough information as NAs or set them to 0s.

```{r}
# TODO: Convert Awards to 2 numeric columns: wins and nominations
#there are four patterns "n/Nominated for #" "# nomination" "w/Won #" "# win"
subsetmatch$Awards[subsetmatch$Awards=="N/A"]=as.numeric(0)#deal with N/A
sum(subsetmatch$Awards!=0) #13033
#for wins
wins=sapply(subsetmatch$Awards, function(x) regmatches(x,gregexpr("(on\\s[0-9]+)|([0-9]+\\swin)",x))[[1]])
wins=sapply(wins, function(x) sum(as.numeric(unlist(regmatches(x,gregexpr("[0-9]+",x))))))
subsetmatch$wins=wins
#for nominations
nominations=sapply(subsetmatch$Awards, function(x) regmatches(x,gregexpr("(ominated\\sfor\\s[0-9]+)|([0-9]+\\snomination)",x))[[1]])
nominations=sapply(nominations, function(x) sum(as.numeric(unlist(regmatches(x,gregexpr("[0-9]+",x))))))
subsetmatch$nominations=nominations
```

**Q**: How did you construct your conversion mechanism? How many rows had valid/non-zero wins or nominations?

**A**: There are 13033 rows has valid wins or nominations. There are four patterns "n/Nominated for #" "# nomination" "w/Won #" "# win". Therefore, I matched those patterns and extracted out numbers and summed them into wins and nominations.

```{r}
# TODO: Plot Gross revenue against wins and nominations
attach(mtcars)
par(mfrow=c(1,2))
ggplot(subsetmatch, aes(x=wins, y=Gross)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
ggplot(subsetmatch, aes(x=nominations, y=Gross)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
```

**Q**: How does the gross revenue vary by number of awards won and nominations received?

**A**: The win-gross chart shows that there is no clear linear relationship between the number of wins and gross. The nomination-gross chart shows that there is a linear relationship between the number of nominations and gross before a threshold, then the relationship becomes diverse afterward.

## 7. Movie ratings from IMDb and Rotten Tomatoes

There are several variables that describe ratings, including IMDb ratings (`imdbRating` represents average user ratings and `imdbVotes` represents the number of user ratings), and multiple Rotten Tomatoes ratings (represented by several variables pre-fixed by `tomato`). Read up on such ratings on the web (for example [rottentomatoes.com/about](https://www.rottentomatoes.com/about) and [ www.imdb.com/help/show_leaf?votestopfaq](http:// www.imdb.com/help/show_leaf?votestopfaq)).

Investigate the pairwise relationships between these different descriptors using graphs.

```{r}
# TODO: Illustrate how ratings from IMDb and Rotten Tomatoes are related
#Here, I focuses on IMDb avearge ratings (imdbRating) and Tomato ratings (tomatoRating)
summary(subsetmatch$imdbRating)#min 1.1;1st 5.6;median 6.4; mean 6.24; 3rd 7.1; max 9.8
summary(subsetmatch$tomatoRating)#min 0; 1st 4.8; median 6; mean 5.86; 3rd 7; max 9.8
attach(mtcars)
par(mfrow=c(1,2))
ggplot(data=subsetmatch, aes(subsetmatch$imdbRating))+geom_density()
ggplot(data=subsetmatch, aes(subsetmatch$tomatoRating))+geom_density()

```

**Q**: Comment on the similarities and differences between the user ratings of IMDb and the critics ratings of Rotten Tomatoes.

**A**: Similarly, the difference between median and mean of both ratings is small, which indicated that there are no outstanding outliers. Differently, the distribution of IMDb is fat-tail while the distribution of Tomato is long-tail.

## 8. Ratings and awards

These ratings typically reflect the general appeal of the movie to the public or gather opinions from a larger body of critics. Whereas awards are given by professional societies that may evaluate a movie on specific attributes, such as artistic performance, screenplay, sound design, etc.

Study the relationship between ratings and awards using graphs (awards here refers to wins and/or nominations). 

```{r}
# TODO: Show how ratings and awards are related
attach(mtcars)
par(mfrow=c(2,2))
#IMDb rating vs wins
ggplot(subsetmatch, aes(x=imdbRating, y=wins)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
#IMDb rating vs nominations
ggplot(subsetmatch, aes(x=imdbRating, y=nominations)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
#Tomato rating vs wins
ggplot(subsetmatch, aes(x=tomatoRating, y=wins)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
#Tomoto rating vs nominations
ggplot(subsetmatch, aes(x=tomatoRating, y=nominations)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
```

**Q**: How good are these ratings in terms of predicting the success of a movie in winning awards or nominations? Is there a high correlation between two variables?

**A**: Those ratings are not good for predicting the success of a movie because we could not see a clear linear relationship. But for tomato ratings, there is a rating range, during which higher rating could predict more wins. I tried to compute the correlation, but the results are NAs. The charts did not show a high correlation. 

## 9. Expected insights

Come up with two new insights (backed up by data and graphs) that is expected. Here “new” means insights that are not an immediate consequence of one of the above tasks. You may use any of the columns already explored above or a different one in the dataset, such as `Title`, `Actors`, etc.

```{r}
# TODO: Find and illustrate two expected insights
subsetrated <- subset(subsetmatch, subsetmatch$Rated=="R"|subsetmatch$Rated=="N-17")
#imdbRating ~ Gross
attach(mtcars)
par(mfrow=c(1,2))
ggplot(subsetrated, aes(x=imdbRating, y=Gross)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
#tomatoRating ~ Gross
ggplot(subsetrated, aes(x=tomatoRating, y=Gross)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
```

**Q**: Expected insight #1.

**A**: Restricted movie rating (R and N-17): these movie ratings seriously restrict the audiences and might impact the profitability of the movie. My hypothesis is that the positive linear relationship will be obvious for these movies. The plots also show it.

**Q**: Expected insight #2.

**A**: My hypothesis is that ratings from IMDB will have different impacts on gross when comparing with the impact of ratings from Tomato. The charts show it. Also, for IMDB rating, the positive linear relationship become obvious after the rating is larger than 7.5, while for tomato rating, the linear relationship is very smooth (slope is small).


## 10. Unexpected insight

Come up with one new insight (backed up by data and graphs) that is unexpected at first glance and do your best to motivate it. Same instructions apply as the previous task.

```{r}
# TODO: Find and illustrate one unexpected insight
subsetdirectorsum <- aggregate(wins~Director, subsetmatch, sum)
names(subsetdirectorsum)[2] <- "sum"
subsetdirectornum <- aggregate(wins~Director, subsetmatch, length)
names(subsetdirectornum)[2] <-"num"
subsetdirector <- merge(subsetdirectorsum,subsetdirectornum)
subsetdirector <- as.data.frame(subsetdirector) 
ggplot(subsetdirector, aes(x=num, y=sum)) + geom_point(shape=1) # sum is number of wins; num is number of movies directed by the director
```

**Q**: Unexpected insight.

**A**: I am interested in the relationship between the number of movies that one director directed and the number of wins that one director receives for the movies. My hypothesis is that "no pains, no gains", which means that you have more chance to get awards if you produced more movies. But it's not the truth. You can see that some directors created more than 150 movies, but the number of awards is almost 0. Therefore, we must put quality before quantity. If there are more data about the gender of directors, it would be awesome to investigate the gender issue in the film production field.

